%----------------------------------------------------------------------------------------
%  ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
  \addchaptertocentry{\acknowledgementname}

  I would like to express my deepest gratitude and appreciation for \supname, my supervisor, for his invaluable guidance and support throughout the process of completing my academic thesis. His expertise, commitment, and insightful feedback have been instrumental in shaping this work and have significantly contributed to my growth as a researcher. His encouragement and patience, particularly during challenging times, have been a source of inspiration and motivation.
  It proved, indeed, to be a privilege to work under his supervision.
  
  I would also like to sincerely appreciate the academic environment and resources provided by \emph{\univname}. The stimulating scholarly community, state-of-the-art facilities, and access to extensive research materials have played an indispensable role in shaping my research journey.
  
  I would like to thank the \emph{\deptname} for providing me with the opportunity to pursue my graduate studies. The input and feedback provided by the faculty members have been invaluable in helping me develop my research skills.
  I must also acknowledge the facilities and resources provided by the \emph{\deptname}, particularly the \href{https://varuna.aero.iitb.ac.in/ace/}{\emph{Aerospace Computational Engine - ACE}} HPC cluster, which has been crucial to the completion of this work.
  
  I would also like to thank the members of the lab group headed by \supname for their support and guidance. Amal S Sebastian, Abhinav Muta, Asmelash Haftu, Pawan Negi, and Navaneet \textit{(in no particular order)} helped provide an environment conducive to learning and growth. I must acknowledge their generous sharing of knowledge and encouragement.
  Their contributions have enriched my research experience and have made this journey more enjoyable.
  
  Lastly, I extend my heartfelt gratitude to my family and friends for their unwavering support, understanding, and patience throughout this academic pursuit. Their unconditional love and encouragement have been my source of strength and motivation.

\end{acknowledgements}